---
title: "HW 1 448"
output:
  pdf_document: default
---

##2a)This question is a regression problem, because we are looking at predicting a numerical value. We are most interested in inference for this problem.n = 500 and p = 3 (profit, number of employees, and industry)

##b)This question is a classification problem, because we are looking at predicting a non-numeric categorical value. We are most interest in 
 # prediction. 
 #n = 20 
 #p = 13 (price charged, marketing budget, competition price, +10 others)

##c) 
##This question is a regression because we are looking at the percent change, 
 # which is a numerical value. We are most interested in predicting for the % 
 # change 
 # n = 52 (weeks in a year for the year 2012)
 # p = 4 (USD/EURO, USD, GB, and Germany % change)




#4a) 
### Spam email class example: Response is Yes or No for Spam. 
 #Predictors: How many characters in the email (key words)
 #inference because we are making conclusions based on existing data/evidence
### Should an applicant be accepted into SFSU: Response is Admitted or Not 
  #Admitted. Predictors include: GPA, SAT Scores, Applicant Essay. The goal is 
  #prediction. 
### Covid Vaccination status to enter an arena/event is another example of 
  #classification. The response is vaccinated versus unvaccinated. Predictors 
  #can include whether they have their vaccine card or not. The goal is 
  #prediction for this scenario because we do not have previous data and we are 
  #predicting for a y.

##b) 
### Predicting Sales for a quarter/year. Using last year's data to create a 
  #prediction on this year's data. The response is a numerical value that is
  #somewhat close to the last year data. Our predictors can be many different
  #things, it all depends on the company service?product/etc. This is a 
  #prediction because we are using multiple different factors to predict a y. 
### Predicting the value of a stock price. The response is also a numerical 
  #value that is either higher or lower than what we predict. Predictors for
  # the stock market can include: inflation rate, overall economy, etc.
  #This is also a prediction problem because we are predicting for some var. y. 
### The last example in which we can use regression is predicting the true 
  #value of a home. We can use past data and current data to predict the price. 
  # The response variable is the price of the home. Some predictors include: 
  # location, square footage, inflation rate, etc. Similar to the previous 2 
  # reasonings, this is also a prediction problem. 

##c)
### One real life application for using cluster analysis can be for determining 
  #natural disasters: Learning about different regions that are affected 
  #we can determine such danger zones, awaring the public of a possible threat. 
###Another example is for clustering is used in Cities. Understanding Carbon 
  #footprint we can identify which areas/zones are high in CO2. 
###One final example for using cluster analysis is City construction. 
  #We can identify certain regions and locations, allowing companies to 
  #establish a proper price for each value. 


#8
```{r}
#a
college = read.csv("College.csv")


#b
rownames = college[, 1]
View(college)

college1 = college[, -1]
View(college1)

#c
summary(college1)
college1$Private = as.factor(college1$Private)
pairs(college1[,1:10])

plot(college1$Private, college1$Outstate)

Elite = rep("No", nrow(college1))
Elite[college1$Top10perc > 50] = "Yes"
Elite = as.factor(Elite)
college1 = data.frame(college1, Elite)
summary(college1$Elite)  #78 Elite Universities 
plot(college1$Elite, college1$Outstate) #box-plot

par(mfrow = c(2,2))
hist(college1$Apps, main = "Number of Applications")
hist(college1$Personal, main = "Personal Cost")
hist(college1$Books, main = " Book Cost")
hist(college1$Grad.Rate, main = "Graduation Rate (%)")

plot(college1$Grad.Rate, college1$Outstate, xlab = "Grad Rate", 
     ylab = "OS tuition", col = "blue")
##The higher the Out of state tuition fees, the higher the graduation rate.
  #This gives indication that students are more likely to graduate if their
  #tuition fees are higher. This can equate to nursing majors, medical majors. 
  #Even tech majors today which require a lot more schooling than other jobs.
```


#10
```{r}
##a
#install.packages('ISLR2', repos = "http://cran.us.r-project.org")
library(ISLR2)
colnames(Boston)
str(Boston)
#There are 506 rows and 13 columns. The rows represent the suburbs of Boston. 
  #The columns represent the predictors. For example, per capita crime rate by 
  #town, proportion of non-retail business acres per town, nitrogen oxide 
  #concentration, etc. 

##b
library(ISLR2)

pairs(Boston)

par(mfrow = c(2,2))
plot(Boston$indus, Boston$crim)
plot(Boston$rm, Boston$medv, col = "blue")
plot(Boston$age, Boston$ptratio)

##Based on these 3 plots, we can see as rm increases, so does the medv. 

##c
par(mfrow = c(2,2))

plot(Boston$age, Boston$crim)
##As the proportion of owner-occupied units built prior to 1940 increase, 
  #so does the crime rate. 
plot(Boston$lstat, Boston$crim)
##As lower status of the population (percent) increase, we see an increase in 
  #the crime rate
plot(Boston$medv, Boston$crim)
##We see that crime rate is much higher in the lower median value of 
  #owner-occupied homes in $1000s. 

##d

hist(Boston$crim, main = "Hist. of per capita crime rate", xlab = "Crime Rate",
     ylab = "Freq.")
###From the above histogram, we see that Boston has some high crime rates.
hist(Boston$tax, main = "Hist. of full-value property-tax rate", ylab = "Freq.")
###From this histogram we can see that some areas in Boston have a higher tax
  # than others. 
hist(Boston$ptratio)
###Some suburbs in Boston have more teachers than others. This can be true due 
  # some areas having a higher population than others, thus a need for more
  # teachers.

##e
#install.packages("tidyverse")
library(tidyverse)
charles.river = filter(Boston, chas ==1 )
count(charles.river) #There are a total 35 suburbs that bound the Charles River

##f
summary(Boston$ptratio) #The median ratio for pupil-teachers is roughly about 19

##g
library(tidyverse)
#arrange(Boston, medv) ; (DID NOT KNIT THIS, PRINTS 20+ PAGES of DATA)  
###The lowest median value (5) has a crime rate of 38.35%, and an lstat of 30.59.
 # It is also clear to see that these values are higher than their average. 

##h
###average more than 7: 
LJ = filter(Boston, rm > 7)
length(LJ$rm) # 64 suburbs average more than 7 rooms per dwelling. 

###average more than 8:
LJ1 = filter(Boston, rm > 8)
length(LJ1$rm) # only 13 suburbs average more than 8 rooms per dwelling. 

summary(LJ1) # of the 13 suburbs, they have an average crime rate of 71.9%. 
  #the teacher ratio has an average mean of 16.36. The average 
  #median value of owner-occupied homes in $1000s is 44.2 (roughly $44,000)

```

